\chapter{Style Analyser}
\label{cap:analyser}

\chapterquote{- Marty McFly: Wait a minute, Doc. Ah... Are you telling me you built a time machine... out of a DeLorean?\\- Dr. Emmett Brown: The way I see it, if you're gonna build a time machine into a car, why not do it with some style?}{Back to the Future (1985)}

When proposing a model for stylometric analysis of e-mails for recipient-based personalised writing, it is necessary to define parameters which determine and describe the writing style of a user. For this purpose, we have developed a style analyser that extracts the messages written by the user and obtains the value of various metrics from them. Then it will be useful for analysing different user's e-mails and drawing conclusions about what parameters describe the writing style of each person more accurately.

In this section we explain the architecture of this analyser (see Section \ref{section:stylearch}) and each of the modules that compose it (they are explained in Sections \ref{section:extmod} to \ref{sect:analyserclass}). Finally, we present the behaviour of the execution with the Gmail account that is analysed (this discussion can be looked up in Section \ref{section:exebehav}).

\section{Architecture} \label{section:stylearch}
\input{Capitulos/Secciones/AnalyserArchitecture}

\section{Extraction module} \label{section:extmod}
\input{Capitulos/Secciones/ExtractorMod}

\section{Preprocessing module} \label{section:prepmod}
\input{Capitulos/Secciones/PrepMod}

\section{Typographic correction module} \label{section:typomod}
\input{Capitulos/Secciones/TypoMod}

\section{Measuring module} \label{section:measmod}
\input{Capitulos/Secciones/StyleMeasuring}

\section{Analyser class}\label{sect:analyserclass}
\input{Capitulos/Secciones/AnalyserMod}

\section{Execution behaviour} \label{section:exebehav}
After executing it with the Gmail account that is analysed (the author's Gmail account), of the 1084 e-mails extracted, 921 were measured, which represents approximately the $84.96$\% of the total. In this execution, all the 1084 messages were correctly preprocessed, but 163 were discarded in the typographic correction phase. Some of them were discarded because, after the preprocessing, they were missing text, whereas the rest of them did not pass this phase due to its language (there were e-mails written in English) or, a minority because they had a not interested message body for the analysis of the writing style (for example we found some e-mails whose only text was an url).

\section{Conclusions}
In order to measure all the e-mails of a user, we develop a style analyser which has four different phases: extraction (which makes use of Gmail API with the purpose of extracting all the sent messages), preprocessing (which is in charge of transforming the body of the e-mail so the spaCy model can analyse it, for instance by removing the signature or soft break lines introduced due to the message encoding), typographic correction (which detects and corrects the typographic mistakes) and style measuring (which calculates the value of different metrics of each e-mail). The modules which correspond to the last three phases are implemented as web services so they are easily reusable in other projects. Besides, each module is independent to the rest of them. For this reason, it is necessary an \textit{Analyser} class in charge of assembling all these different packages.

After executing the style analyser with a Gmail account, we obtain the metrics of 921 messages. With these results, we can study the effectiveness of each metric to distinguish the different recipients of the messages. In the next chapter, we try to draw conclusions about the obtained metrics.