\chapter{Proposal for a personalised writing model based on the recipient}\label{cap:proposal}

\chapterquote{Science may never come up with a better office communication system than the coffee break}{Earl Wilson}

After analysing the metrics that define the style of the e-mails based on its recipient, we are able to design a system that takes advantage of this knowledge and generates messages according to what we learnt. In this chapter we will explain a proposal for this system with which the user can obtain a text just by providing some keywords related with the topic of the desired e-mail and its recipient. With this in mind, we are going to detail the different phases of our model and its general architecture (see Section \ref{sect:phasemod}). Then, each one of its tasks is going to be explained: searching phase (see Section \ref{sect:searchemail}) and rewriting phase (see Section \ref{sect:transemail}).

\section{Phases of the model}\label{sect:phasemod}
\input{Capitulos/Secciones/ModelPhases}

\section{Searching for the e-mail with the most similarity}\label{sect:searchemail}
\input{Capitulos/Secciones/SearchMod}

\section{Transforming e-mail according to metrics}\label{sect:transemail}
\input{Capitulos/Secciones/Rewriting}

\section{Conclusions}
Taking advantage of the selected eight metrics obtained thanks to the execution of the style analyser, we have proposed a model which generates e-mails based on their recipients. It has two phases: searching phase and rewriting phase. The first one consists of looking for the most similar message to a given set of keywords by using Latent Semantic Indexing. The second is in charge of modifying the body of that e-mail, with the purpose of changing its style according to the eight selected metrics. There are some feasible solutions which can modify the values of those style markers, we suggest four possibilities: to change the number of adjectives, to substitute words for synonyms, to vary the amount of adverbs and to change the number of pronouns. Despite of its possible issues that we can find in this second phase, this designed model is supported by the obtained results and it is a first approaching to a real stylometric e-mail analyser for recipient-based personalised writing.