\chapter{Introduction}
\label{cap:introduccion}

\chapterquote{Have you ever retired a human by mistake?}{Rachael - Blade Runner (1982)}

In this chapter we explain the incentives which motivate us to develop this work (see Section \ref{sect:motiv}) and the objectives which we are going to try to fulfil (see Section \ref{sect:obj}). Finally, the structure of this report is explained in Section \ref{sect:structure}.

\section{Incentive}\label{sect:motiv}
Smartphone development meant not only a technological advance but a social revolution too. These intelligent telephones have brought with them countless paradigm shifts in terms of the social sphere. Since then, we are able to speak of a new model of human relationship both between people and with our technology. This current relation standard is due to the easy and quick way of accessing the different information that our mobile devices provide us. Long waits (nowadays the meaning of ``long'' waits has changed too, people consider more than two or three seconds too much time) for obtaining anything such as accessing to a website or showing any operation result, are excessively tedious and could be even frustrating for some smartphone users. When we are using our mobile, we want, as fast as possible, the information we are looking for. Precisely because of this, Human-Computer Interaction (HCI) becomes a very important part in the process of development of most applications, not only in terms of speed of response and efficiency of algorithms, but also in how we show different information and the easiness for obtaining it.

As for the relationships between people, as we have said, they have dramatically changed. There is no doubt that the main driving technologies behind this transformation of our relational paradigm are the social networks and the instant messaging. Focusing on the latter, it is necessary to make a breakdown of what consequences to our interpersonal interaction the instant communication have brought with itself. Just as it happens with the HCI, easiness and speed are probably the first features we look for when we are going to send or receive any information to anybody. If we also expect a reply, the ideal would be to obtain it as quickly as possible. Therefore, in most of occasions, in practice we are looking for an ``automatic'' response from a human, what practically implies that everyone is ``obligated'' to be connected at any time with the answer we are asking for prepared. This new insight into the relationships between people, that perceives the humans as servers who send a request waiting for a quickly reply with the expected data, has promoted a very fast sending of short messages which intends to substitute and simulate an spoken conversation. These little texts are often concise and summarised, and they form an atomic semantic unit, namely they have their own independent meaning.

This behaviour has transcended other communication services such as the electronic mail, which has greatly grown since its appearance in 1971. Indeed it goes on growing and reaches the number of 306 billions of e-mails sent per day. The e-mail has gone beyond the professional scope and has encroached the personal sphere, which means that we send e-mail messages to our contacts which with we keep both a professional and a personal relation. However, there are significant differences in the written text which depend on the receiver of the information even though the channel is the same. Despite having the concise and summarised nature mentioned, we do not spend the same amount of time to write every e-mail. Perhaps we are more rigorous with the composition of some messages, we change our writing style or we use a formal language. This modification of our way of writing a message depending on the recipient is what we are going to study in this work.

The research of the definition of the writing style based on the recipient of the message through mathematical metrics allow us to know how is necessary to change a text in order to make it appropriate for the audience. Furthermore, the progress in this field of study improves our knowledge about the natural language generation of e-mails, specifically based on the recipient. As we have said, the need of quickly responses becomes clear today. The automatic personalised writing is able to meet the needs of a society which is in constant connection with all the information generated every second. For this reason, the progress in this field of study could be useful for the more than four billion e-mail users.

With these incentives we focus our work on the study of the metrics which describe the writing style of e-mail based on the recipient of it and how it is possible to take advantage of these mathematical objects in order to build a recipient-based personalised writing system.

\section{Objectives}\label{sect:obj}
The main objective of our work is the proposal of a model for stylometric analysis of e-mails for recipient-based personalised writing. This model must measure the writing style of the user and use this information in order to carry out the composition of an e-mail.

To achieve it, we must study the field of stylometry and implement a software which is able to measure the different e-mails from the user's account. Once we have a system which can extract the messages and calculate a set of style metrics of each one, we will have to evaluate the obtained results and study which style markers differentiate better between the different recipients. To obtain this conclusions will allow us to suggest a system that can take into account them and generate e-mails with different styles depending on the receiver of the information.

Furthermore, we will look for developing reusable tools that could be use in other similar projects. With this in mind we will develop some web services which carry out the different task of extracting and measuring the e-mails. In this way, these tools can be easily incorporate to other implementations.

\section{Report structure}\label{sect:structure}
This report is structured in seven chapters. The first one, as we have said, is the introduction of the work, where we give an idea of what we are going to study. Chapter \ref{cap:estadoDeLaCuestion} (State of the Art) presents the knowledge that we are going to use and which are required for the correct understanding of the work. In it, we will explain the communication service which is the centre of our work: the electronic mail, and every aspect of it  which would be useful for our work, such as the protocols that defines it. In addition to the electronic mail, we will study the field of computational stylometry in Chapter \ref{cap:estadoDeLaCuestion}. Specifically, we will delve into the particular characteristics of e-mails as a text document and the most common metrics used for analysed them. This chapter will finish with the explanation of the Latent Semantic Indexing, which is an algorithm that will be required for our final model.

The next Chapter (Used Technologies) presents the technologies used for our software development: Gmail API, spaCy, Flask and MongoDB. The first of them is necessary due to the fact that the e-mail account that we are going to analyse belongs to the Gmail service. As for spaCy, it is a syntactic analyser which will be useful when we are going to measure the text of the e-mail. In respect of Flask and MongoDB, they are popular software tools used for the development of web services and the management of a NoSQL database, respectively. We are going to use them in our software implementation.

As regards Chapter \ref{cap:analyser} (Style Analyser), in it we will explain in detail the developed implementation of the software which is in charge of all the process from the extraction to the measuring of the e-mails of the user. Each of the phases that are part of this task, are explained as well as the style metrics used.

After obtaining the metrics' value of each message, we study the set of data in Chapter \ref{cap:analysis} (Style feature analysis), making use of popular machine learning techniques such as K-Means, Principal Component Analysis and Decision Trees. Besides, the previous preparation of the data is explained.

The penultimate chapter (Proposal for a personalised writing model based on the recipient), takes advantage of all the previous knowledge in order to suggest a model for stylometric analysis of e-mails for recipient-based personalised writing and study its viability.

Finally, in Chapter \ref{cap:conclusiones} (Conclusions and Future Work), we expose the conclusions of the developed work and the possible improvements and extensions which can be carried out with the purpose of going on working in the field of study.